Reproduction Survey Analysis

### 2022-12-07 procedure/code/203_results.Rmd
Update raw results, including frequencies and cross tabs by methods (quant, qual, mixed) and field.

```{r beliefs-stats-by-subfield}
group_by(survey_resp, Q3) %>%
  summarise(
    count = n(),
    mean = mean(belief, na.rm = TRUE),
    sd = sd(belief, na.rm = TRUE)
  )
```

@@

```{r beliefs-anova}
aov(belief ~ Q3, data=survey_resp) %>% summary()
```

>>>>

```{r beliefs-stats-by-subfield}
group_by(survey_resp, Q3_recoded) %>%
  summarise(
    count = n(),
    mean = mean(belief, na.rm = TRUE),
    sd = sd(belief, na.rm = TRUE)
  )
```

@@

```{r beliefs-anova}
aov(belief ~ Q3_recoded, data=survey_resp) %>% summary()
```
